Hysteresis in human computation:\\ how one task affects another

### 2015-01-09 docs/publications/2014.09_SCIENCE/man.tex
proofed latest revisions, updated figures and figure legends

Faced with the ever-growing scale and complexity of data, academic and 
industrial researchers are increasingly relying on \textit{human computation} 
to extract useful knowledge.  Microtask
platforms, like Amazon Mechanical Turk, act like a human compute cluster,
making it possible to access human cognition quickly and inexpensively. 
This has lead to their broad adoption by social and computer scientists.  
Human computation is being used experimentally in applications
where expert opinion would normally be sought, such as in reviewing 
medical images.
Here we show that the repeated performance of similar tasks, an inherent
feature of microtask and crowdsourcing platforms, acts as a strong
and largely unexplored source of bias.  Previous tasks exert strong 
influences on how workers perform later tasks, which we call 
\textit{intertask effects}.  These effects are more severe than effects 
caused by framing, such as by disclosing a task's purpose.  
Using image-labeling, the canonical microtask, we show that prior 
tasks influence the content that workers chose to focus on, as well as the 
richness and specialization of their vocabulary.    
While intertask effects can be a source of systematic bias, our
results suggest that with appropriate task-engineering, it might be possible
to leverage intertask effects to hone worker focus and specificity, helping
to elicit reproducible, expert-level judgments.
\end{sciabstract}

@@

Here we focus on an aspect of the microtask setup that is ubiquitous, but 
has not yet received much attention.  Microtasks are typically distributed 
to workers in bundles.  For example, a worker might be assigned a set of ten 
images, and asked to provide descriptive words (or \textit{labels}) for 
each.  On MTurk, these bundles are called Human Intelligence Tasks (HITs).
But for the sake of clarity, we will use ``task'' to mean the smallest 
repeatable unit of work, which, in our study, consists of labeling a single
image.

Results in psychology show that people are 
susceptible to various kinds of priming 
\cite{BJOP1796,No2007,beller1971priming}, including 
task-repetition effects \cite{Gass1999549,sohn2001task}.  
But to our knowledge, no study has investigated the bias that might
result from the fact that microtask workers typically perform many tasks in 
succession.  The experiments we present here show that a worker's response 
during a task depends strongly on the tasks performed beforehand.
In other words, unlike CPUs and GPUs, HPUs are subject to 
\textit{hysteresis}, meaning that their outputs depend on the 
\textit{history} of their inputs.
We call the effects that prior tasks induce on later ones 
\textit{intertask effects}.

We investigated intertask effects using image-labeling tasks on the Amazon 
Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  This trend will probably continue 
in the long term, because image labeling is still very difficult to automate
\cite{5543192}, and is used in many applications, such as website moderation, 
computer vision research, and social media analytics (\# insert other refs) 
\cite{5543192}.  In our first experiment, which we will refer to as 
\textit{intertask-food-objects}, workers were assigned to either a
\textit{food} or \textit{objects} treatment.  Workers in these treatments
performed a set of five \textit{initial tasks}, which each involved 
providing five descriptive labels for an image depicting 
either food or (non-food) objects, depending on the worker's 
treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
tasks, workers performed five \textit{test tasks}, which were identical for 
both treatments.  The test tasks contained images depicting a 
mixture of food and objects (see Fig.~\ref{fig:task}C), and workers
were again asked to provide five labels.  Five initial 
tasks, together with the test tasks, comprised one HIT 
(\# workers were only allowed to participate once). During the HIT, workers 
were presented images one at a time, and, crucially, there was no distinction
or interruption between the initial and test tasks.

@@

While this affirms the \textit{existence} of intertask effects, we wish to
understand the nature and severity of the bias induced by prior task 
exposures.  
We define the extent of bias, $\theta$, induced by alternative exposures, to 
be the resulting change in the probability with which workers provide given 
responses (formally the total variation distance):
\begin{equation}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p_1(x) - p_2(x) \right|,
\end{equation}
where $p_i(x)$ is the probability that a worker subjected to treatment $i$
provides response $x$, from the set of possible responses $X$.
It is important to emphasize that a sigificant result from a $\chi^2$ test 
only allows us to conclude that $\theta$ is non-zero.  Determining $\theta$ from finite samples of 
responses, using purely statistical approaches, is difficult (\#), which 
leads us to reformulate the
problem in terms of classification: given a worker's 
response, can a machine reliably infer what her prior task-exposure had 
been?  Intuitively, the greater the effect that prior tasks have on subsequent
responses, the more accurate the classifier can be.  Formally, as we show
in the supplementary text, the accuracy of such a classifier, $\eta$,
yields a lower bound on the bias:
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
Thus, measuring the accuracy of a classifier allows us to establish a
lower bound on the extent of bias. This approach can be used to bound the 
bias induced by any perturbation, including both intertask effects and 
framing.  As we have defined it, bias ranges from 0 (meaning the exposures 
do not affect the probabilities of respnoses), to 1 
(or 100\%) (meaning that under different exposures, workers provide completely
different sets of responses).

\begin{figure}
	\centering
	\includegraphics[scale=0.6]{figs/images.pdf}
	\caption{
		Examples of images used for various experiments and treatments:
		(A) initial task for \textit{task1:food}, (B) initial task for 
		\textit{task1:obj}, (C) test task for treatments in \textit{exp1}, 
		(D) initial task for \textit{task2:food}, 
		(E) initial task for \textit{task2:cult},  
		(F) test task for treatments in \textit{exp2}.  
		The full set of experimental materials is shown in the 
		supplementary text.
	}

@@

Using a na\"ive Bayes classifier (\# in the 
supplementary material we discuss the choice of classifier, the
approach to measuring accuracy, and draw a comparison to the results obtained 
if a support vector machine is used), we found that intertask effects 
lead to a 30\% bias between workers from the \textit{food} and 
\textit{objects} treatments.

There has been considerable interest in the effects that framing can have
on microtask responses
\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
as a point of comparison, we performed a similar experiment 
in which we framed the purpose of the tasks.  In the experiment 
\textit{frame-food-objects}, workers were either told that 
the tasks were ``Funded by the laboratory for the visual perception of Food 
and Ingredients'', or ``\ldots of Objects and Tools''.  
Framing did induce statistically significant changes in the frequencies of 
word usage (as determined by $\chi^2$ test; $p=0.0012$), albeit at a much 
lower significance than for intertask effects.  But we did not find a 
significant amount of framing-induced bias, using a na\"ive Bayes classifier 
(see Fig.~\ref{fig:theta}).  This suggests that prior task exposure is a 
stronger priming modality than framing.

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (\#) (see Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin 
(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
strong bias as a result of intertask effects (about 50\%) 
(see Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
framing, by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or culture.  
For this framing experiment, we did not observe a statistically significant 
difference between the labels attributed by the \textit{food} and 
\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).

@@

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Bias as measured by a na\"ive Bayes classifier, $\theta_\mathrm{NB}$,
		induced in image-labeling tasks, due to framing and 
		intertask effects. 
		(A) Bias in the responses to five test tasks,
		measured between the pairs of treatments indicated on the $x$-axis.  
		(B) Bias between the treatments of \textit{task1}, 
		measured for individual test tasks, and plotted as a function of 
		task position.  Error bars show the 95\% confidence intervals.
	}
	\label{fig:theta}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
	\caption{
		Intertask and framing effects on the vocabulary workers use to refer 
		to food(\#), when labeling images, for various treatment pairs.
		(A) Relative change in the number references to food. 
		(B) Relative change in the number of \textit{unique} 
		references to food (lexical richness). 
		(C) Relative specialization of food references, based on the 
		hypernym-hyponym relations (this calculation is shown in the 
		supplementary text).  For all
		plots, a positive bar height indicates that the \textit{*:food}
		treatment has more of the quantity than its conjugate treatment.
	}
	\label{fig:specificity}
\end{figure}

To better understand the nature of 
intertask effects, we investigated the vocabulary
that workers used to label test tasks. A natural expectation is that, within
a given experiment, the food-primed workers would use more food-related words 
than their non-food-primed counterparts.  However, this was not generally 
the case. In the \textit{intertask-food-culture} experiment, food-primed
workers actually used significantly \textit{fewer} food-related words 
during test tasks
(\# food related words were identified using the wordnet corpus, augmented
with additional words obtained by crawling a recipe website (see supplementary
information for details)) (see Fig.~\ref{fig:specificity}).  This finding
rules out a simple mechanism in which worker's attention is drawn toward
content that had been found in earlier tasks.  Seeing content in prior tasks 
seems to affect the probability that a worker refers to that content it in 
subsequent tasks, but does not necessarily increase it.

To deepen our understanding, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related words
used.  Even if workers provide an abundance of food-related words, if the 
same words are often repeated, there will of course be a smaller total 
diversity.  This could happen, for example, if workers use generic references 
to food.
Both \textit{intertask} experiments showed that food-exposed workers had 
greater lexical richness, in reference to food, than their non-food-primed 
counterparts (as much as 20\% more) (see Fig.~\ref{fig:specificity}).  
The increase in lexical richness in the case of 
\textit{intertask-food-culture} is quite interesting, because in that 
experiment, food-primed workers made fewer total references to food.  
We also observed enrichment of the food-related lexicon in the 
\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
although to a lesser extent.

The observations regarding lexical richness lead us to suspect that 
initial tasks might influence workers to use more refined or specialized 
words, when refering to aspects of content that had been present in the 
initial tasks (i.e. food).  This would help explain why, in the case of 
\textit{intertask-food-culture}, we observed a significantly greater 
\textit{diversity} of food-related words despite their significantly lesser 
\textit{total amount}.
To test whether exposure to food in initial tasks increased the specialization
of food-references, we used the wordnet corpus to operationalize the 
notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
relations between \# English nouns.  Hypernyms are generalizations 
(for example, ``bread'' is a hypernym for 
``pumpernickel''), while hyponyms are specializations.
For each experiment, we compared food-related words provided by workers from 
one treatment to those from the other, and tallied the excess number of cases
where one treatment's words were more specialized than the other.
Expressed as a percentage of their total, this tally served to 
measure the relative specialization of the vocabulary used in one 
treatment's vocabulary relative to the other 
(\# full detail for this calculation is provided the supplementary text) 
(see Fig.~\ref{fig:specificity}).

In all experiments except \textit{frame-food-culture}, food-primed workers 
used significantly more specialized words than their non-food-primed 
counterparts (about 15\% more; see Fig.~\ref{fig:specificity}C).
It is interesting that such substantial increases in both the lexical 
richness and specialization of food-related words 
held for \textit{intertask-food-culture}, where, as mentioned, we observed 
that food-exposed workers had made \textit{fewer} references to food overall. 
These observations point 
to countervailing factors: one factor tending to activate the more 
specialized and less common food-related words 
(yielding greater lexical richness and specialization), and the other tending 
to suppress certain, presumably more common and generic words 
(yielding fewer food-related words in total).

@@

Prior to this study, little thought appears to have been given to the 
ordering and bundling of microtasks.  But our findings show that these are 
powerful design factors.  A natural response to our findings 
might be simply to randomize task ordering, a practice that is commonly 
employed.  But the sheer extent of bias that we observed leads us to question 
whether that is the best approach.  Although the bias is random in 
that case, it is still on the order of 30-50\%, which is a major contribution
to noise in the results.  It would be preferable to understand intertask
effects in greater depth so that they might \textit{controlled} rather than
simply randomized.

Our findings suggest that, through careful task engineering,
it might be possible to achieve greater quality and reproducibility
of responses.  
A consistent goal in human computation is the achievement of expert-level
judgments from non-expert workers (\#).  This has been achieved in some
applications (\#). The distinction between experts and novices can be 
attributed in part to the posession of specialized knowledge and heuristics. 
But to a large degree, this distinction lies in the ability of 
experts to direct their focus toward salient features, while filtering out 
non-salient ones \cite{kellman2009perceptual}.  Using strategic exposure to
prior tasks, it might be possible to guide workers' focus and salience 
attribution, enabling expert-level judgment in a wider variety of 
crowdsourced applications.
We anticipate that future work will yield techniques to control intertask 
effects, enabling one to both reduce unwanted bias, as well as tune the 
focus, diversity, and specificity of worker responses.

@@

	\end{tabular}
	\caption{
		Top 5 words, used to label the first test image, whose usage frequency
		increased or decreased the most between treatments of given 
		experiments.  Positive values indicate that the food-exposed treatment
		used the word with higher frequency.  Word frequencies for 
		\textit{intertask-food-objects} are aggregated accross 5 
		permutations, and hence tend to show larger absolute differences.
	}
	\label{table:top-words}
\end{table}

@@

	Before performing any analysis on the labels that workers provided, we
	performed a series of preprocessing steps.  
	Labels that contained
	multiple words (separated by spaces or punctuation) were split, with
	punctuation removed, and the separated words were treated as distinct 
	features in subsequent analysis.
	Misspelled words were automatically corrected using a spelling 
	correction algorithm described below.  
	Next, words were lematized using the
	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
	Common words such as ``the'', ``to'', or ``with'', were found using the
	the NLTK's English stop-word list and removed \cite{loper2002nltk}.

@@

	\paragraph{Variance in food vocabulary size (lexical richness).}
	The number of unique words in a text is strongly dependant on the size
	of the text: as more text is sampled, previously unseen words continue
	to be found, though at a decreasing rate.  This means that when the 
	lexical richness is measured for a large and small sample, they are not 
	actually estimates of the same quantity.  It is not clear that drawing 
	confidence intervals around the lexical richness measured at one sample 
	size is meaningful, nor is it easily done.

>>>>

Faced with the ever-growing scale and complexity of data, academic and 
industrial researchers are increasingly relying on \textit{human computation} 
to extract useful knowledge.  Microtask
platforms, like Amazon Mechanical Turk, act like a human compute cluster,
making it possible to access human cognition quickly and inexpensively. 
This has lead to their broad adoption by social and computer scientists.  
Human computation is being used experimentally in applications
where expert opinion would normally be sought, such as in reviewing 
medical images.
Here we show that the repeated performance of similar tasks, an inherent
feature of microtask and crowdsourcing platforms, acts as a strong
and largely unexplored source of bias.  The effects that earlier tasks exert
on later ones are more severe than effects caused by framing, 
such as by disclosing a task's purpose.  
Using image-labeling, the canonical microtask, we show that prior 
tasks influence the content that workers chose to focus on, as well as the 
richness and specialization of their vocabulary.    
While intertask effects can be a source of systematic bias, our
results suggest that with appropriate task-engineering, it might be possible
to leverage intertask effects to hone worker focus and specificity, helping
to elicit reproducible, expert-level judgments.
\end{sciabstract}

@@

Here we focus on a ubiquitous feature of the microtask setup: the 
tendency for microtask workers to perform many tasks in quick succession. 
Even if a worker performs the minimum possible amount of work, 
she will likely have performed several microtasks, since they are typically 
distributed to workers in bundles.  For example, in one bundle, a worker 
might be assigned a set of ten images, and asked to provide descriptive words 
(or \textit{labels}) for each.  On MTurk, these bundles are called Human 
Intelligence Tasks (HITs), but for the sake of clarity, we will use 
``task'' to mean the smallest repeatable unit of work, which, in our study, 
consists of labeling a single image.

The repetitive completion of tasks is of concern because people's responses
to a prompt can be strongly influenced by their recent exposure to stimuli,
due to the well-known phenomenon of \textit{priming} 
\cite{BJOP1796,No2007,beller1971priming}.  Priming is typically relevant when 
the prior stimuli bear some conceptual or perceptual connection to the 
ensuing task, and so, the repetition of similar tasks within the typical 
microtask setup creates an ideal context for strong priming effects
\cite{Gass1999549,sohn2001task}.

Researchers investigating a somewhat similar class of psychological phenomena,
found that ratings that microtask workers give to items in a list
depend on the order in which the list is presented, an effect known as
\textit{positional bias} \cite{lerman2014leveraging}.  While this 
result applies mainly to tasks of a 
particular design, it shows that basic psychological phenomena
can profoundly influence crowdsourced data.  If human computation is to be
understood as a kind of computing architecture, it will certainly be 
necessary to account for the computational ramifications of these 
psychological phenomena at play in the HPU.

The results we present here show that a worker's response during a task
does indeed depend strongly on the tasks performed beforehand.   
In engineering terms, 
unlike CPUs and GPUs, HPUs are subject to \textit{hysteresis}, meaning
that their outputs depend on the history of their inputs.  Because 
task-repetition is inherent in their design, virtually all microtask studies,
and most crowdsourced studies are at risk from the form of bias we 
investigate here. We call the effects that earlier tasks exert on later ones 
\textit{intertask effects}.

We investigated intertask effects using image-labeling tasks on the Amazon 
Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
the most common MTurk tasks 
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}. 
This trend is likely to continue 
in the long run, because image labeling is still very difficult to automate
\cite{5543192}, and is used in many applications, such as website moderation, 
computer vision research, and social media analytics (\# insert other refs) 
\cite{5543192}.  In our first experiment, which we will refer to as 
\textit{intertask-food-objects}, workers were assigned to either a
\textit{food} or \textit{objects} treatment.  Workers in these treatments
performed a set of five \textit{initial tasks}, which each involved 
providing five descriptive labels for an image depicting 
either food or (non-food) objects, depending on the worker's 
treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
tasks, workers performed five \textit{test tasks}, which were identical for 
both treatments.  The test tasks contained images depicting a 
mixture of food and objects (see Fig.~\ref{fig:task}C), and workers
were again asked to provide five labels.  Five initial 
tasks, together with the test tasks, comprised one HIT 
(\# workers were only allowed to participate once). During the HIT, workers 
were presented images one at a time, and, crucially, there was no distinction
or interruption between the initial and test tasks.

@@

While this affirms the \textit{existence} of intertask effects, we wish to
understand the nature and severity of the bias induced by prior task 
exposures.  To this end, we define the extent of bias, $\theta$, induced by 
alternative exposures, to 
be the resulting change in the probability with which workers provide given 
responses (\# this is a general divergence metric between probability 
distributions known as the \textit{total variation distance}):
\begin{equation}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p_1(x) - p_2(x) \right|,
\end{equation}
where $p_i(x)$ is the probability that a worker subjected to treatment $i$
provides response $x$, from the set of possible responses $X$.
It is important to emphasize that a significant result from a $\chi^2$ test 
only allows us to conclude that $\theta$ is non-zero.  Determining $\theta$ from finite samples of 
responses, using purely statistical approaches, is difficult (\#), which 
leads us to reformulate the
problem in terms of classification: given a worker's 
response, can a machine reliably infer what her prior task-exposure had 
been?  Intuitively, the greater the effect that prior tasks have on subsequent
responses, the more accurate the classifier can be.  Formally, as we show
in the supplementary text, the accuracy of such a classifier, $\eta$,
yields a lower bound on the bias:
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
By measuring the accuracy of a classifier, we can bound the 
bias induced by any perturbation, including both intertask effects and 
framing.  As defined, bias ranges from 0 (meaning the exposures 
do not affect the probabilities of responses), to 1 
(or 100\%) (meaning that under different exposures, workers provide completely
different sets of responses).

\begin{figure}
	\centering
	\includegraphics[scale=0.6]{figs/images.pdf}
	\caption{
		Examples of images used in
		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
		\textit{objects} treatments of \textit{intertask-food-objects};
		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
		\textit{frame-food-objects};
		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
		\textit{culture} treatments of \textit{intertask-food-culture};
		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
		\textit{frame-food-culture}.
		The full set of experimental materials is shown in the 
		supplementary text.
	}

@@

Using a na\"ive Bayes classifier (\# in the 
supplementary material we discuss the choice of classifier, the
approach to measuring accuracy, and draw a comparison to the results obtained 
if a support vector machine is used), we found that intertask effects 
lead to a 30\% bias between workers from the \textit{food} and 
\textit{objects} treatments.  This represents a substantial potential to 
distort microtask data.

There has been considerable interest in the effects that framing can have
on microtask responses
\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
as a point of comparison, we performed a similar experiment 
in which we framed the purpose of the tasks.  In the experiment 
\textit{frame-food-objects}, workers were either told that 
the tasks were ``Funded by the laboratory for the visual perception of Food 
and Ingredients'', or ``\ldots of Objects and Tools''.  
Framing did induce changes in the frequencies of 
word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
the \textit{extent} of framing-induced bias we found was insignificant 
(see Fig.~\ref{fig:theta}).  This suggests 
that prior task exposure is a stronger priming modality than framing.

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (see Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin 
(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
strong bias as a result of intertask effects (about 50\%) 
(see Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
framing, by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or culture.  
For this framing experiment, we did not observe a statistically significant 
difference between the labels attributed by the \textit{food} and 
\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).

@@

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
		classifier, induced in image labeling tasks,
		(\textbf{A}) by exposing workers to initial tasks or framing. 
		As workers proceed through test tasks, the effects of initial tasks 
		wane, as shown (\textbf{B}) for \textit{intertask-food-objects}, but 
		remain significant even after five tasks.  Standard error bars are 
		shown.
	}
	\label{fig:theta}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.94]{figs/vocab_specificity.pdf}
	\caption{
		(\textbf{A}) Exposing workers to initial tasks and framing 
		involving food changed how often they referred to food 
		during test tasks, but did not always increase it (in all three plots,
		positive values indicate a larger quantity for food-exposed workers).
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, except in the 
		case of \textit{frame-food-culture} (stars indicate the threshold
		for a significant deviation from the null hypothesis, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers also used more specialized words to refer to food.
		Standard error bars are shown in (\textbf{A} and \textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

To better understand the nature of 
intertask effects, we investigated the vocabulary
that workers used to label test tasks. A natural expectation is that, during
the test tasks within
a given experiment, the food-primed workers would use food-related words 
more often than their non-food-primed counterparts.  However, this was not 
generally 
the case. In the \textit{intertask-food-culture} experiment, food-primed
workers actually used significantly \textit{fewer} food-related words 
during test tasks
(\# food related words were identified using the wordnet corpus, augmented
with additional words obtained by crawling a recipe website (see supplementary
information for details)) (see Fig.~\ref{fig:specificity}).  This finding
rules out a seemingly-simple mechanism in which workers emphasize
content that had been present in earlier tasks.  Seeing content in prior tasks
affects the probability that a worker refers to it in subsequent tasks, but 
does not necessarily \textit{increase} the probability.

To deepen our understanding, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related words
used.  Even if workers provide an abundance of food-related words, if the 
same words are often repeated, there will of course be a smaller 
diversity.  This could happen, for example, if workers use generic references 
to food.
Both \textit{intertask} experiments showed that food-exposed workers had 
greater lexical richness, in reference to food, than their non-food-primed 
counterparts (as much as 20\% more) (see Fig.~\ref{fig:specificity}).  
The increase in lexical richness in the case of 
\textit{intertask-food-culture} is quite interesting, because in that 
experiment, food-primed workers made fewer total references to food.  
We also observed enrichment of the food-related lexicon in the 
\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
although to a lesser extent.

The observations regarding lexical richness lead us to suspect that 
initial tasks might influence workers to use more refined or specialized 
words, when referring to aspects of content that had been present in the 
initial tasks (i.e. food).  This would help explain why, in the case of 
\textit{intertask-food-culture}, we observed a significantly greater 
\textit{diversity} of food-related words despite their significantly lesser 
\textit{total amount}.
To test whether exposure to food in initial tasks increased the specialization
of food-references, we used the wordnet corpus to operationalize the 
notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
relations between \# English nouns.  Hypernyms are generalizations 
(for example, ``bread'' is a hypernym for 
``pumpernickel''), while hyponyms are specializations.
For each experiment, we compared food-related words provided by workers from 
one treatment to those from the other, and tallied the excess number of cases
where one treatment's words were more specialized than the other, as a 
percentage of the total (see Fig.~\ref{fig:specificity}B) (\# full detail for 
this calculation is provided the supplementary text).

In all experiments except \textit{frame-food-culture}, food-primed workers 
used significantly more specialized words than their non-food-primed 
counterparts (about 15\% more; see Fig.~\ref{fig:specificity}C).
It is interesting that such substantial increases in both the lexical 
richness and specialization of food-related words 
held for \textit{intertask-food-culture}, where, as mentioned, we observed 
that food-exposed workers made \textit{fewer} references to food overall. 
These observations point 
to countervailing factors: one factor tending to activate the more 
specialized and less common food-related words 
(yielding greater lexical richness and specialization), and the other tending 
to suppress certain, presumably more common and generic words 
(yielding fewer food-related words in total).

@@

Prior to this study, little thought appears to have been given to the 
ordering and bundling of microtasks.  But our findings show that these are 
powerful design factors.  A natural response might be simply to randomize 
task ordering, a practice that is commonly employed.  But the sheer extent of 
bias that we observed leads us to question 
whether that is the best approach.  Although the bias would be random in 
that case, it is still on the order of 30-50\%, which is a major contribution
to noise in the results.  It would be preferable to understand intertask
effects in greater depth so that they might \textit{controlled} rather than
simply randomized.

Our findings suggest that, through careful task engineering,
it might be possible to achieve greater quality and reproducibility
of responses.  
A consistent goal in human computation is the achievement of expert-level
judgments from non-expert workers (\#).  This has been achieved in some
applications (\#). The distinction between experts and novices can be 
attributed in part to the possession of specialized knowledge and heuristics. 
But to a large degree, this distinction lies in the ability of 
experts to direct their focus toward salient features, while filtering out 
non-salient ones \cite{kellman2009perceptual}.  Using strategic task 
exposures, it might be possible to guide workers' focus and salience 
attribution, enabling expert-level judgment in a wider variety of 
crowdsourced applications.
We anticipate that future work will yield techniques to control intertask 
effects, enabling one to both reduce unwanted bias, as well as tune the 
focus, diversity, and specificity of worker responses.

@@

	\end{tabular}
	\caption{
		Top 5 words, used to label the first test image, whose usage frequency
		increased or decreased the most between treatments of given 
		experiments.  Positive values indicate that the food-exposed treatment
		used the word with higher frequency.  Word frequencies for 
		\textit{intertask-food-objects} are aggregated across 5 
		permutations, and hence tend to show larger absolute differences.
	}
	\label{table:top-words}
\end{table}

@@

	Before performing any analysis on the labels that workers provided, we
	performed a series of preprocessing steps.  
	Labels that contained
	multiple words (separated by spaces or punctuation) were split, with
	punctuation removed, and the separated words were treated as distinct 
	features in subsequent analysis.
	Misspelled words were automatically corrected using a spelling 
	correction algorithm described below.  
	Next, words were lemmatized using the
	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
	Common words such as ``the'', ``to'', or ``with'', were found using the
	the NLTK's English stop-word list and removed \cite{loper2002nltk}.

@@

	\paragraph{Variance in food vocabulary size (lexical richness).}
	The number of unique words in a text is strongly dependent on the size
	of the text: as more text is sampled, previously unseen words continue
	to be found, though at a decreasing rate.  This means that when the 
	lexical richness is measured for a large and small sample, they are not 
	actually estimates of the same quantity.  It is not clear that drawing 
	confidence intervals around the lexical richness measured at one sample 
	size is meaningful, nor is it easily done.
